---
title: "day1-exercises"
output: html_document
date: "2022-12-01"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Module 1 Exercise

- Create an R script which performs the following three tasks:

  - Create, store, and display a sequence of values from 5 to -11 that progresses in steps of 0.3.
  - Repeat the vector c(-1,3,-5,7,-9) twice, with each element repeated 10 times, store and display the result, then display the result, sorted from the largest value to the smallest.
  - Create, store, and display a vector containing 15 valuesin a sequence from 10 to 19.

```{r}
# Module 1 Exercise

# a. Create and store a sequence of values from 5 to -11 that progresses in steps of 0.3

a <- seq(from=5,to=-11,by=-0.3)
a

# b. Repeat the vector c(-1,3,-5,7,-9) twice, with each element repeated 10 times, and store the result. Display the result sorted from largest to smallest.

b <- rep(x=c(-1,3,-5,7,-9),times=2, each=10)
b

# sort will display sorted vector
sort(b,decreasing=T)

# c. Create a vector containing 15 values in a sequence from 10 to 19

c <- seq(from=10,to=19,length.out=15)
c
```
