---
title: "day3-exercises"
output: html_document
date: "2022-12-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Module 9 Exercise 1

- Use the mtcars dataset to model fuel efficiency, measured in miles per gallon (MPG), in terms of the overall weight of the vehicle (in thousands of pounds).

- Plot the data—mpg on the y-axis and wt on the x-axis.

- Fit the simple linear regression model. Add the fitted line to the plot.

- Interpret the point estimate of the slope. Is the effect of wt on mean mpg estimated to be statistically significant?

- Produce a point estimate and associated 95 percent PI for a car that weighs 6,000 lbs. Do you trust the model to predict observations accurately for this value of the explanatory variable? Why or why not?

```{r}

```

### Module 9 Exercise 2

A cryptocurrency broker is interested in predicting NFT (non-fungible token) sales from advertising. The data is provided in the tab-separated text file NFTSales.txt found in this module.

adverts: The independent predictor variable; the amount invested in advertising for 200 NFTs before release.

sales: The dependent variable, NFT Sales (in dollars) the week after release

Run a regression analysis on this data as you did in Programming Assignment 9A and show the results of a prediction if the broker invests $2500 in advertising.


```{r}

```

