---
title: "day3-exercises"
output: html_document
date: "2022-12-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Module 9 Exercise 1

- Use the mtcars dataset to model fuel efficiency, measured in miles per gallon (MPG), in terms of the overall weight of the vehicle (in thousands of pounds).

- Plot the data—mpg on the y-axis and wt on the x-axis.

- Fit the simple linear regression model. Add the fitted line to the plot.

- Interpret the point estimate of the slope. Is the effect of wt on mean mpg estimated to be statistically significant?

- Produce a point estimate and associated 95 percent PI for a car that weighs 6,000 lbs. Do you trust the model to predict observations accurately for this value of the explanatory variable? Why or why not?

```{r}
# mtcars-analysis.R
# Use the mtcars dataset to model fuel efficiency, measured
# in miles per gallon (MPG), in terms of the overall weight
# of the vehicle (in thousands of pounds).
#
# Plot the data-mpg on the y-axis and wt on the x-axis.
#
plot(mtcars$mpg~mtcars$wt,xlab="Weight (lbs/1000)",ylab="MPG")
# Fit the simple linear regression model. Add the fitted line to the plot.
#
carfit <- lm(mpg~wt,data=mtcars)
carfit
abline(carfit,lwd=2)
#
# Interpret the point estimate of the slope. Is the effect of
# wt on mean mpg estimated to be statistically significant?
#
summary(carfit) # mean MPG = 37.28 - 5.34*weight
#
# For each extra 1000lbs of weight, the mean MPG decreases by
# 5.34; p-value for slope is very small---result is statistically
# significant---strong evidence to suggest that mean MPG changes
# according to weight.
#
# Produce a point estimate and associated 95 percent PI for a car
# that weighs 6,000 lbs. Do you trust the model to predict
# observations accurately for this value of the explanatory
# variable? Why or why not?
#
predict(carfit,newdata=data.frame(wt=6),interval="prediction",level=0.95)
#
# Predicting at 6000lbs seems untrustworthy. Extrapolation is far enough
# outside the range of the observed data such that the associated prediction
# interval has a lower limit that is negative, which makes no sense in
# terms of the response variable of MPG.
```

### Module 9 Exercise 2

A cryptocurrency broker is interested in predicting NFT (non-fungible token) sales from advertising. The data is provided in the tab-separated text file NFTSales.txt found in this module.

adverts: The independent predictor variable; the amount invested in advertising for 200 NFTs before release.

sales: The dependent variable, NFT Sales (in dollars) the week after release

Run a regression analysis on this data as you did in Programming Assignment 9A and show the results of a prediction if the broker invests $2500 in advertising.


```{r}
# NFTSales.R

# read the data
NFTSales <- read.table('NFTSales.txt',sep='\t', header=TRUE)

# plot the data
plot(NFTSales$sales ~ NFTSales$adverts, xlab='Advertising $', ylab='Sales $')

# linear regression
NFTSales.lm <- lm(sales~adverts,data=NFTSales)

# show the fit line
abline(NFTSales.lm,lwd=2)

# summarize and predict for 2500
summary(NFTSales.lm)
predict(NFTSales.lm, newdata=data.frame(adverts=2500), interval="prediction",level=0.95)
```

